---
title: "A UN Report on the Relationship between GDP and CO2 emissions"
author: "Jade Bowers"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse) #contains ggplot package
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

```{r gdp_lifeExp_1997}
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp) +
  geom_point(aes(color = continent, size = pop/1000000)) +
  scale_color_brewer(palette = "Set1") +
  labs(x = "GDP per Capita", y = "Life Expectancy", 
       title = "Do people in wealthy countries live longer?", 
       size = "Population (in millions)")
```

